Improving content discovery through combining linked data and data mining techniques

### 2015-12-22 report/report.tex
Trying to finish maximal pipeline diagram.

@@

@@

        IRI -> RDF1 [label="parse"];
        IRI -> RDF2 [label="extract"];
        IRI -> RDF3 [label="scrape"];

@@

        RDF -> RDFp1 [label="dereference/parse"];
        RDF -> RDFp2 [label="hypernym inference"];
        RDF -> RDFp3 [label="expert inference"];
        RDF -> RDFp4 [label="OWL inference"];

@@

        RDF -> Features [label="generate"];
      }
    \end{dot2tex}
  \end{center}
  \caption{\label{fig:maximal-pipeline}Maximal Data Pipeline}
\end{sidewaysfigure}

>>>>

%TODO

@@

%TODO

%TODO

@@

        IRI -> RDF1 [label="\text{parse}"];
        IRI -> RDF2 [label="\text{extract}"];
        IRI -> RDF3 [label="\text{scrape}"];

@@

        RDF -> RDFp1 [label="\text{dereference/parse}"];
        RDF -> RDFp2 [label="\text{hypernym inference}"];
        RDF -> RDFp3 [label="\text{expert inference}"];
        RDF -> RDFp4 [label="\text{OWL inference}"];

@@

        RDFp -> Features [label="generate"];
      }
    \end{dot2tex}
  \end{center}
  \caption{\label{fig:maximal-pipeline}Maximal Data Pipeline}
\end{sidewaysfigure}

\section{Pipeline Architecture}
